Reply to referees for CQG-105854

### 2019-04-17 EchoesV2.tex
Ready for submission...

In Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large} we see the asymptotic behavior of two solutions with $\sigma=0.9185r_g$ and $\sigma=5.196r_g$, respectively. Observing that the amplitude of the echoes is not large in general, since it varies depending on the spectral content of the initial pulses, which are not the same in the case of initial Gaussian wavelets with different widths. In analogy with the scalar case, we notice in the upper corner of both figures that the amplitude of the echoes does not decay exponentially in time.
\par
\begin{figure*}
\centering
\subfigure{
\includegraphics[width=.45\textwidth]{figures/Echo_sigma_odd_l_2.pdf}} \,
\subfigure{
\includegraphics[width=.45\textwidth]{figures/Echo_sigma2_odd_l_2.pdf}} 
\caption{\label{fig:echo_sigma_odd} Left panel: Amplitudes of the first four echoes of $\Psi^{\mathrm{odd}}_{20}$ as a function of $\sigma$ for $\ell=2$. Right panel: Relative amplitude of the first four echoes compared to the amplitude of the transient. The points represent the simulated double/single wall pairs used in our analysis, as in Fig.~\ref{fig:echo_sigma}. These results are not significantly different for $\Psi^{\mathrm{even}}_{20}$. At low widths, the transient decreases faster than the amplitudes of the echoes as $\sigma$ becomes smaller.} 
\end{figure*}

@@

Motivated by the drastic change in the amplitudes of the echoes seen in Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large}. We now explore the dependence of the amplitude of each individual echo with the width of the incident Gaussian pulse. To do so, we follow the same procedure explained by the end of subsection \ref{subsec:wh}: we construct a logarithmic grid in $\sigma$, centered at $\sigma_{\mathrm{DW}}=\sqrt{27}r_g/2\ell$ and spaced in intervals of $\sqrt{2}\sigma_{\mathrm{DW}}$. In addition to this, we define the variable $\Delta\Psi^{\mathrm{odd}}_{\mathrm{clean}}\equiv\Psi^{\mathrm{odd}}_{\mathrm{original}}-\Psi^{\mathrm{odd}}_{\mathrm{bh}}$ in order to clean the solutions from backscattering effects coming from the potential tails, which complicate the task of determining the amplitudes of the echoes with high $\sigma$/low frequency. Once the solutions are clean, the most effective way to find the maxima of each echo is by calculating the local maxima of the Hilbert envelope for the clean signal. In this case, the Hilbert envelopes are the green curves in the upper corner of Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large} and the maxima are the red dots on top of each curve. 
This labor is even more computationally expensive than in the scalar case, not only because we are solving the scattering problem for two systems -- one with a single potential barrier and another with the potential cavity -- but also we are now working with the two polarizations (i.e., the even and odd solutions). Our results of the amplitude analysis in Fig.~\ref{fig:echo_sigma_odd} show the existence of a value of $\sigma$ maximizing the amplitude of the echoes. This is compatible with the notion of a band of widths/frequencies in which the echoes have sufficient amplitude to be measured.

@@

In this paper, we show that in general, the echoes do not have a large amplitude as we can see directly in the left panel of Fig.~\ref{fig:asympt_two_sigmas} and in Fig.~\ref{fig:odd_sigma_large}, where we also observe that the amplitude of the echoes does not decay exponentially in time. In addition to this, we found that there is a thin band of preferred frequencies (and the widths of the corresponding ingoing Gaussian signals) where the amplitude of the echoes is maximized. Such a frequency band is centered around the ``sweet spot'' in which the coefficients of transmissivity and reflectivity overlap, and it is precisely where the QNMs peaks are squeezed in. We extended our analysis to find the range in which the width of the incident pulses maximize the amplitude of the first four echoes, and how large is their amplitude compared to the transient. For small widths, this ratio could be as large as 0.15, we should notice, however, that the amplitude of the transient gets also suppressed in this range. In Figs.~\ref{fig:echo_sigma} and \ref{fig:echo_sigma_odd}, we found that for low widths of the ingoing signal, as the widths become smaller, the transient decreases faster than the amplitude of the echoes. In the study of the gravitational wave scattering by a Morris-Thorne wormhole, we find small differences between the Regge-Wheeler and the Zerilli effective potentials, as depicted in the right panel of Fig.~\ref{fig:evenodd_potentials}. As it is visible in Fig.~\ref{fig:pol}, such a difference modifies the polarization of any ingoing wave in a way analog to the dispersion across an optically active medium, opening the possibility of studying gravitational wave polarimetry.

>>>>

In Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large} we see the asymptotic behavior of two solutions with $\sigma=0.9185r_g$ and $\sigma=5.196r_g$, respectively. Observing that the amplitude of the echoes is not large in general, since it varies depending on the spectral content of the initial pulses, which are not the same in the case of initial Gaussian wavelets with different widths. In analogy with the scalar case, we notice in the upper corner of both figures that the amplitude of the echoes does not decay exponentially in time.
\par
\begin{figure*}
\centering
\subfigure{
\includegraphics[width=.45\textwidth]{figures/Echo_sigma_odd_l_2.pdf}} \,
\subfigure{
\includegraphics[width=.45\textwidth]{figures/Echo_sigma2_odd_l_2.pdf}} 
\caption{\label{fig:echo_sigma_odd} Left panel: Amplitudes of the first four echoes of $\Psi^{\mathrm{odd}}_{20}$ as a function of $\sigma$ for $\ell=2$. Right panel: Relative amplitude of the first four echoes compared to the amplitude of the transient. The points represent the simulated double/single wall pairs used in our analysis, as in Fig.~\ref{fig:echo_sigma}. At small widths, the transient decreases faster than the amplitudes of the echoes as $\sigma$ becomes smaller.} 
\end{figure*}

\begin{figure}[t!]
\centering
\includegraphics[width=.45\textwidth]{figures/Odd_echo_w_t2.pdf}
\caption{\label{fig:echo_long} Asymptotic solution of an ingoing Gaussian pulse with $\sigma=16~r_g$ after its dispersion by a Morris-Thorne wormhole with a longer throat (with a length of 100~$r_g$). The amplitude of the transient is three orders of magnitude larger than the first echo, showing that the echoes do not have a generically large magnitude.}
\end{figure}

@@

Motivated by the drastic change in the amplitudes of the echoes seen in Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large}. We now explore the dependence of the amplitude of each individual echo with the width of the incident Gaussian pulse. To do so, we follow the same procedure explained by the end of subsection \ref{subsec:wh}: we construct a logarithmic grid in $\sigma$, centered at $\sigma_{\mathrm{DW}}=\sqrt{27}r_g/2\ell$ and spaced in intervals of $\sqrt{2}\sigma_{\mathrm{DW}}$. In addition to this, we define the variable $\Delta\Psi^{\mathrm{odd}}_{\mathrm{clean}}\equiv\Psi^{\mathrm{odd}}_{\mathrm{original}}-\Psi^{\mathrm{odd}}_{\mathrm{bh}}$ in order to clean the solutions from backscattering effects coming from the potential tails, which complicate the task of determining the amplitudes of the echoes with high $\sigma$/low frequency. Once the solutions are clean, the most effective way to find the maxima of each echo is by calculating the local maxima of the Hilbert envelope for the clean signal. In this case, the Hilbert envelopes are the green curves in the upper corner of Figs.~\ref{fig:odd_sigma_small} and \ref{fig:odd_sigma_large} and the maxima are the red dots on top of each curve. 
This labor is even more computationally expensive than in the scalar case, not only because we are solving the scattering problem for two systems -- one with a single potential barrier and another with the potential cavity -- but also we are now working with the two polarizations (i.e., the even and odd solutions). Our results of the amplitude analysis in Fig.~\ref{fig:echo_sigma_odd} show the existence of a value of $\sigma$ maximizing the amplitude of the echoes. This is compatible with the notion of a band of widths/frequencies in which the echoes have sufficient amplitude to be measured.\\

\textcolor{red}{The length of the throat for a Morris-Thorne wormhole is an additional parameter of the effective potential cavity. Thus, we simulated the scattering of an arbitrary Gaussian pulse with $\sigma=16~r_g$ by a Morris-Thorne wormhole with a larger throat ($100~r_g$, which is more than two times larger than the cavity used in the previous sections of this paper). In Fig.~\ref{fig:echo_long}, we show that the transient has a slightly larger magnitude consistent with a cavity made out of potential barriers reflective to lower frequencies. The shape of these potential barriers is not different from the walls depicted in Fig.~\ref{fig:evenodd_potentials}, therefore it is still possible to find a frequency ``sweet spot'' for each wall. Moreover, the amplitude of the echoes is three orders of magnitude smaller than the transient, which is coherent with the results shown in this manuscript.}

@@

In this paper, we show that in general, the echoes do not have a large amplitude as we can see directly in the left panel of Figs.~\ref{fig:asympt_two_sigmas}, \ref{fig:odd_sigma_large} and \ref{fig:echo_long}, where we also observe that the amplitude of the echoes does not decay exponentially in time. In addition to this, we found that there is a band of preferred frequencies (and the widths of the corresponding ingoing Gaussian signals) where the amplitude of the echoes is maximized. Such a frequency band is centered around the ``sweet spot'' in which the coefficients of transmissivity and reflectivity overlap, and it is precisely where the QNMs peaks are squeezed in. We extended our analysis to find the range in which the width of the incident pulses maximize the amplitude of the first four echoes, and how large is their amplitude compared to the transient. For small widths, this ratio could be as large as 0.15, we should notice, however, that the amplitude of the transient gets also suppressed in this range. In Figs.~\ref{fig:echo_sigma} and \ref{fig:echo_sigma_odd}, we found that for low widths of the ingoing signal, as the widths become smaller, the transient decreases faster than the amplitude of the echoes. In the study of the gravitational wave scattering by a Morris-Thorne wormhole, we find small differences between the Regge-Wheeler and the Zerilli effective potentials, as depicted in the right panel of Fig.~\ref{fig:evenodd_potentials}. As it is visible in Fig.~\ref{fig:pol}, such a difference modifies the polarization of any ingoing wave in a way analog to the dispersion across an optically active medium, opening the possibility of studying gravitational wave polarimetry.

### 2019-04-17 reply_v1.tex
Ready for submission...

\begin{abstract} 
Thanks to the valuable comments of the referees, we had the chance to review our calculations and solve any potential source of confusion. We have updated our draft in order to accommodate all the comments and objections made to the previous version of our manuscript. 
\end{abstract}
\maketitle

@@

@@

\textbf{Reply:}
Thanks for bringing these papers to our attention. All the references suggested were added in the latest draft of our paper. It is interesting to notice that the Morris-Thorne wormhole eventually evolves into a black hole, as noticed by Wang et al. in arxiv:1802.02003. In addition to this, the idea of a Dyson-series expansion presented by Correia et al. in arXiv:1802.07735 is related to the geometric expansion we suggested in our manuscript.\\

@@

\textbf{Reply:} We have derived in Eq. (12) a more general expression for the geometrical series, now considering the different reflection and transmission coefficients for each potential wall. Furthermore, we used these general expressions to derive the reconstruction series for a system with two identical walls in Eq. (14).\\

@@

\textbf{Reply:} We agree with the referee on this comment, we have now clarified that Eq.(21) only refers to the coefficients of each individual wall, but not the whole system.\\

@@

\textbf{Reply:} In Fig. 17, we have included our results after modelling a cavity with a larger throat distance of 100 $r_g$. Showing that, after filtering the signal, the amplitude of the outgoing echoes is five orders of magnitude smaller than the magnitude of the transient. Which agrees with our result.\\

>>>>

\begin{abstract} 
Summary: Thanks to the valuable comments of the referees, we had the chance to review our calculations and solve any potential source of confusion. We have updated our draft to accommodate all the comments and objections made to the previous version of our manuscript. We worked throughout the following points: (1) Emphasis on the generation of a small net polarization as one of the main results of our paper, by mentioning this finding from the beginning of the manuscript. (2) We included all the suggested references in both the text and the bibliography. (3) The geometrical optics reconstruction formula was generalized to consider walls with different reflectivities and transmissivities. (4) The concept of reflection and transmission coefficients only refer to an individual potential barrier. (5) We also mentioned the ``pinching off'' of the Morris-Thorne solution in larger timescales. (6) We simulated the scattering of a Gaussian pulse of GW towards a ``longer'' wormhole throat (the length of the throat is now $100 r_g$), finding again that the magnitude of the outgoing pulse is not generically large. 
\end{abstract}
\maketitle

@@

\textbf{Comment:} ...I struggled to find what is the main original contribution of this manuscript... In the end, I concluded that the remarks on possible polarization changes are potentially the most significant outcome of their efforts.\\

\textbf{Reply:} We agree that the small net polarization of GW is one of the main results of our manuscript, and we should include it in the body of the paper instead of being in an Appendix. Due to this, this is now appearing in Section III. Additionally, we included it in the introduction of our paper as one of our results.\\

@@

\textbf{Reply:}
Thanks for bringing these papers to our attention. All the references suggested were added in the latest draft of our paper (in addition to some others). It is interesting to notice that the Morris-Thorne wormhole eventually evolves into a black hole, as noticed by Wang et al. in arxiv:1802.02003. In addition to this, the idea of a Dyson-series expansion presented by Correia et al. in arXiv:1802.07735 is related to the geometric expansion we suggested in our manuscript.\\

@@

\textbf{Reply:} We derived in Eq. (12) a more general expression for the geometrical series, now considering the different reflection and transmission coefficients for each potential wall. Furthermore, we used these general expressions to derive the reconstruction series for a system with two identical walls in Eq. (14).\\

@@

\textbf{Reply:} We agree with the referee on this comment, we have now clarified that Eq.(21) only refers to the coefficients of each individual wall, but not the whole system. Nevertheless, this definition is sufficient to perform the analysis followed in our manuscript since the system we study is constituted by two identical walls.\\

@@

\textbf{Reply:}  We have simulated the collision of a wavepacket (and the corresponding time evolution plot) towards a cavity with a longer throat distance of 100 $r_g$ (more than two times bigger than the original length), we chose an arbitrary initial Gaussian pulse with $\sigma=16r_g$. Showing in Fig. 17 -- before Subsection IIA -- that the amplitude of the outgoing echoes is three orders of magnitude smaller than the transient, which is coherent with our result. All of these details have been incorporated in the text of our latest draft.\\
